\Title

### 2023-02-09 Grimaldi-etal-BiolCybernetics.tex
Methods : 2

\subsubsection{Applied on this detection task}

@@

\begin{equation}\label{eq:kernel_b}
\forall \presynaddr \in \presynaddrspace^{\synapse^\postsynaddr}, \forall \timev \in T, \; \;
\mathcal{C}^\postsynaddr(\presynaddr,\timev)
= \sum_{\ranksyn  \in [1, N_{\synapse^\postsynaddr}]} \kernel^\postsynaddr(\presynaddr_\ranksyn, \synapticdelay_\ranksyn) \cdot A(\presynaddr, \timev-\synapticdelay_\ranksyn)
\end{equation}

where $\presynaddrspace^{\synapse^\postsynaddr}$ is the address space of the receptive field of neuron $\postsynaddr$ and $N_{\synapse^\postsynaddr}$ is the number of synapses belonging to neuron $\postsynaddr$. To benefit from invariance to location observed in CNN and to simplify the implementation of the model, one assumes that kernels should be similar across different positions and define a convolution operator. The characteristics of the kernels are shared among one class of neurons such that $\forall i,j \in [1, N_\class]^2, \; \kernel^i_\class = \kernel^j_\class$. The computational brick used in equation~\eqref{eq:kernel_b} can be extended to every position, in space and time, of the boolean matrix $A$:

>>>>

\subsubsection{Application to the motion detection task}

@@

\begin{equation}\label{eq:kernel_b}
\forall \presynaddr \in \presynaddrspace^{\synapse^\postsynaddr}, \forall \timev \in T, \; \;
\mathcal{C}^\postsynaddr(\presynaddr,\timev)
= \sum_{\ranksyn  \in [1, N_{\synapse^\postsynaddr}]} \kernel^\postsynaddr(\presynaddr_\ranksyn, \synapticdelay_\ranksyn) \cdot A(\presynaddr, \timev-\synapticdelay_\ranksyn)
\end{equation}
where $\presynaddrspace^{\synapse^\postsynaddr}$ is the address space of the receptive field of neuron $\postsynaddr$ and $N_{\synapse^\postsynaddr}$ is the number of synapses belonging to neuron $\postsynaddr$. To benefit from invariance to location observed in CNN and to simplify the implementation of the model, one assumes that kernels should be similar across different positions and define a convolution operator. The characteristics of the kernels are shared among one class of neurons such that $\forall i,j \in [1, N_\class]^2, \; \kernel^i_\class = \kernel^j_\class$. The computational brick used in equation~\eqref{eq:kernel_b} can be extended to every position, in space and time, of the boolean matrix $A$:
